One possible solution to the dark matter and the hierarchy problem is achieved
introducing a symmetry, called \gls{susy}~\cite{SUSYIntro}, that relate fermions
and bosons. Supersymmetry is capable of solving the hierarchy problem by
canceling out the quantum corrections that bring $m_H$ close to $\Lambda$ thus
restoring the naturalness of the SM\@. SUSY introduces a set of new particles
that are the \emph{superpartners} of the SM ones. These supersymmetric particles
or \emph{sparticles} have the same quantum numbers and couplings of their SM
counterpart but turn with a supersymmetry transformation a spin 1/2 fermionic SM
particle into a bosonic spin 0 sparticle and a spin 1 SM boson in a spin 1/2
fermion. The supersymmetric bosons are called \emph{sleptons}, adding the ``s'
prefix (that stands for ``scalar') to their SM fermionic partners and are
denoted with a ``$\textasciitilde$' on top of their symbol, so for example the
SM electrons are called \emph{selectrons} and denoted with
$\tilde{e}_\mathrm{\, L}$ and $\tilde{e}_\mathrm{\, R}$ where the R and L does
not refer to their helicity (being 0-spin bosons) but to that of their SM
superpartners. Similarly for \emph{smuons} and \emph{staus}:
$\tilde{\mu}_\mathrm{\, L}$, $\tilde{\mu}_\mathrm{\, R}$,
$\tilde{\tau}_\mathrm{\, L}$, $\tilde{\tau}_\mathrm{\, R}$ and for the
\emph{squarks}: $\tilde{q}_\mathrm{\, L}$, $\tilde{q}_\mathrm{\, R}$ (with
$q = u,\, d,\, s,\, b,\, c,\, t$). The supersymmetric fermions are called
\emph{gauginos}, adding the ``ino' suffix to the SM gauge bosons, for instance,
the $W$ and $Z$ bosons have the \emph{wino} ($\widetilde{W}$) and \emph{zino}
($\widetilde{Z}$) superpartners, the photon has the \emph{photino}
($\widetilde{\gamma}$) and the Higgs field has the \emph{Higgsino}
($\widetilde{H}$). In addition to these new particles, the minimal
supersymmetric extension of the Standard Model, called
\gls{mssm}~\cite{MSSMIntro}, introduces three neutral and two charged Higgs
bosons leading to five physical Higgs states. The neutral superpartners of these
Higgs states ($\widetilde{H}^{\, 0}$), combine with the bino and the wino
($\widetilde{B}$, $\widetilde{W}^{\, 0}$)in four new mass eigenstates called
\emph{neutralinos} ($\widetilde{\chi}^{\, 0}_{\, i}$ with $i = $~1, 2, 3,
4). The charged higgsinos ($\widetilde{H}^{\, +}$, $\widetilde{H}^{\, -}$) and
the winos ($\widetilde{W}^{\, +}$, $\widetilde{W}^{\, -}$) mix and give rise to
two mass eigenstates of charge $\pm 1$ called \emph{charginos}
($\widetilde{\chi}^{\, \pm}_{\, i}$ with $i = $~1, 2). In the MSSM framework a
new multiplicative factor can be introduced, the R--parity, that also explains
the stability of the proton and is defined as:
\begin{equation}
  \label{eq:91}
  R = (-1)^{3(B - L) + 2S}
\end{equation}
where $B$ and $L$ are the baryon and lepton numbers respectively and $S$ is the
spin. It can be seen that all SM particles have $R = + 1$ while supersymmetric
particles have $R = -1$. The conservation of R--parity has important
phenomenologiacal consequences:
\begin{itemize}
\item The \gls{lsp} is stable.
\item The final decay products of SUSY particles are an odd number.
\item In collider experiments sparticles can only be produced in pairs.
\end{itemize}
If the LSP is stable and electrically neutral (dark) and interacts only weakly
with matter it makes a good candidate for non--baryonic dark
matter~\cite{WIMPS}. In the MSSM, good LSP candidates are either the neutralino
or the gravitino, the supersymmetric partner of the graviton (the hypothesised
gravitational gauge boson).

No sparticle has been observed at the colliders so far, hinting that they must
have a bigger mass than their SM counterparts in fact, if the had the same mass
they would have already been produced at the colliders, this imply that SUSY is
a \emph{broken symmetry}. Detecting one of these supersymmetric particles would
shed light on some of the SM shortcomings and thus many searches at the current
colliders focus their attention on finding SUSY particles.
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../search_for_DM_LED_with_ATLAS"
%%% End:
