In general the physics search strategy for new phenomena can be outlined in four
steps, the first one is to define an \emph{hypothesis test}, the \emph{null
  hypothesis} is that no signal is present and the \emph{alternate hypothesis}
is that it exists. The next steps are meant to quantify which one of the
hypotheses is favored by experimental observations, to this end it is necessary
to identify the observables of the experiment, next a \emph{test--statistic} (a
function of these observables) of the known background and to be tested signal
is defined to rank the experiments from the least to the most
signal--like. Finally a rule to quantify the significance of the exclusion or
discovery is chosen.

In the monojet analysis the observable of the experiment is the number of events
in the signal region defined with the criteria illustrated in
Section~\ref{sec:event-selection}, the $\met$ is the test--statistic and a
\gls{cl} of 95\% is chosen for the exclusion. The number of events observed in
the signal region is governed by a Poisson distribution
\begin{equation}
  \label{eq:86}
  P(O|E) = \frac{E^O }{O!} e^{- E}
\end{equation}
where $O$ is the number of observed events and $E$ is the number of expected
events. In absence of signal (background only hypothesis), the expected number
of events is the total number of predicted background events. If some signal is
present (signal plus background hypothesis), the expected number of events is
given by the predicted number of background events plus the predicted number of
signal events. In terms of Poisson distribution, the probability of observing up
to $N_\mathrm{\, SR}$ events in the SR in a signal plus background hypothesis
is:
\begin{equation}
  \label{eq:87}
  P(N_\mathrm{\, SR}|S+B) = \sum^{N_\mathrm{\, SR}}_{k = 0} \frac{(S + B)^k}{k!}
  e^{- (S + B)},
\end{equation}
if this probability is low, the null hypothesis is likely to be the right one
or, in other words, the lower this probability is, the more likely is that the
tested signal is not present in the SR and the hypothesis of it explaining some
physics process can be excluded. To quantify the significance of the exclusion a
CL is calculated as:
\begin{equation}
  \label{eq:88}
  CL_\mathrm{\, S+B} = 1 - P(N_\mathrm{\, SR}|S+B) = 1 - \alpha
\end{equation}
where typically $\alpha = 0.05$ and a 95\% CL$_\mathrm{\, S+B}$ is quoted. The
maximum number of expected signal events (S$_\mathrm{\, max}$)for which
CL$_\mathrm{\, S+B}$ < 0.95 can be calculated and if the number of expected
signal events ($S$) exceeds this value (S > S$_\mathrm{\, max}$), the model can
be excluded~\cite{PawelThesis}. In the monojet analysis the CL$_\mathrm{\, S}$
method~\cite{CLsMethod} is used, where:
\begin{equation}
  \label{eq:89}
  CL_\mathrm{\, S} = \frac{CL_\mathrm{\, S+B}}{CL_\mathrm{\, B}}.
\end{equation}
This method addresses cases where there is a small signal rate or the BG is
compatible with the expected signal.
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../search_for_DM_LED_with_ATLAS"
%%% End:
