My contribution to the ATLAS experiment started in early 2013 by studying the
electronic noise in the hadronic calorimeter. The Tile Calorimeter is designed
to measure jets, tau particles, missing energy and for the energy reconstruction
of hadrons, thus having an up--to--date description of the noise in the detector
is important for most physics analysis in ATLAS. During the reprocessing of the
2011 data I developed a set of python scripts in order to plot the noise
constants variation over several calibration runs. Based on these scripts I
carried out new studies of noise evolution some of which are described in
\cref{cha:noise-studies-with}. The performance of the ATLAS TileCal were
presented in a poster at the ``XXVII International Symposium on Lepton Photon
Interactions at High Energies (2015)'' and appear in the proceedings of the
conference on the ``Proceedings of Science''.

\mbox{}

I later started analyzing the ATLAS data joining the monojet team in the effort
of trying to answer relevant Standard Model open questions. During Run~I my
contribution was limited to the study of some of the systematic uncertainties
associated to the cross section for extra dimension models. In Run~II the ATLAS
software framework was radically changed along with the data format thus the
Stockholm analysis code had to be largely rewritten. I am the main contributor
to this software that allows to produce end--user last analysis stage ROOT files
from the ATLAS centrally produced data sets.

In the Run~II analysis an upper cut on the number of jets was introduced, the
efficiency of such a cut was studied using a multivariate method based on the
TMVA package and the results, being in agreement with other studies performed in
the group, implemented in the analysis. The expected limits and the sensitivity
of the SUSY compressed spectra scenario with $\squarkprod$ were for the first
time estimated by me in the monojet analysis and lately compared to the observed
limit in the 3.2~$\ifb$ collected by ATLAS during Run~II data taking. The
results of this study are summarized in the paper in ref.~\cite{MonoJetPaper}.
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../search_for_DM_LED_with_ATLAS"
%%% End:
