The energy resolution of a detector measure its capability of distinguishing
between radiation of similar energies; the better the energy resolution, the
better it can separate energy peaks belonging to different decays.

The energy resolution, in general, can be written as:
\begin{equation}
  \label{eq:64}
  \frac{\sigma_E}{E} = \frac{a}{\sqrt{E}} \oplus \frac{b}{E} \oplus c,
\end{equation}
where the $\oplus$ symbol indicates a quadratic sum. The first term in the
equation is the \emph{stocastic term}, it is due to fluctuations related to the
physical development of the shower. In homogeneous calorimeters, this term is
small because the energy deposited in the active volume by a monochromatic beam
of particles is constant for each event. In a sampling calorimeter, the active
layers are interleaved with absorber layers thus the energy deposited in the
active material fluctuates event by event. These are called \emph{sampling
  fluctuations} and represent the greatest limitation to energy resolution in
these kind of calorimeters due to the variation in the number of charged
particles which cross the active layers. The second term in eq.~\eqref{eq:64} is
called the \emph{noise term}, it comes from the electronic noise of the detector
readout chain. Sampling or homogeneous calorimeters which collect the signal in
the form of light, using for example a photo-multiplier tube with a high gain
multiplication of the signal with a low electronic noise, can achieve low levels
of noise. Calorimeters that collect the signal in form of charge, must use an
pre-amplifier having thus a higher level of noise. In sampling calorimeters, the
noise term can be further reduced by increasing the sampling fraction, this way
there is a larger signal coming from the active material and a higher
noise-to-signal ratio. The last term of the equation is the \emph{constant
  term}, it does not depend on the energy of the particles but includes all the
non uniformities in the detector response such as instrumental effect, radiation
damage, detector aging or the detector geometry~\cite{Calorimetry}.
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../search_for_DM_LED_with_ATLAS"
%%% End:
